### 2025-09-29 src/articles/article3.qmd
sync google docs changes

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the time specified by the Excuse Plan.
1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with @sec-art-H23EB4B2, Item 1) will count as an unexcused absence.

@@

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary with the possibility of suspension.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

>>>>

1. Excuses for chapter meetings must be submitted in writing to the Secretary according to the method and time specified by the Excuse Plan.
1. Excuses must be approved by a {{< var glossary.simple-majority >}} vote of Executive Council ({{< var acronyms.ec >}}).
1. Failure to {{< var glossary.attend >}} a chapter meeting without an approved excuse (in accordance with @sec-art-H23EB4B2, Item 1) will count as an unexcused absence.

@@

1. A brother who has three unexcused absences in a row must be brought up for standards by the Secretary in accordance with Article V, Section 2, Item j.1 of the IBL.
1. A brother who has three unexcused absences throughout the semester will be {{< var glossary.staggard >}}.
1. A brother who has four unexcused absences throughout the semester will be placed on {{< var glossary.probation >}} until the end of the semester.
1. A brother who has seven unexcused absences throughout the semester will be brought up for standards by the Secretary with the possibility of suspension.

### 2025-09-29 src/articles/article6.qmd
sync google docs changes

1. The Treasurer will present a preliminary budget to the Budget Committee (@sec-art-VI2T9PVL, Item 2c) no later than six weeks before the beginning of the Fall Semester.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
1. Budget Committee
   a. The Budget Committee (@sec-art-VI2T9PVL, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
   a. Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).

@@

1. Each brother, New Member, and Alumnus is {{< var glossary.responsible >}} for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
   a. Any decision regarding this rule will be decided by {{< var acronyms.ec >}}.
1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
1. Brothers may send a notice directly to the president that they will not be paying dues for the coming semester. One month after this notice has been sent, the brother is automatically suspended.

@@

1. {{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).

@@

   a. The chair who controls the budget in question.
      i. If the budget is not under a particular chair, or the chair is indisposed, the president may act as a substitute.
      i. If the chair who controls the budget is also the treasurer, any other member of {{< var acronyms.ec >}} may act as a substitute.

>>>>

1. The Treasurer will present a preliminary budget to the Budget Committee (@sec-art-VI2T9PVL, Item 2c)  and CAB Treasurer Advisor no later than one month before the end of the previous semester.
   a. The Budget Committee will work with the treasurer to create a budget to be submitted to the chapter.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to CAB.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
   a. Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).
1. Safety Margin and Emergency Fund
   a. Any money leftover for the year from the Safety Margin must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).

@@

1. Each brother, New Member, and Alumnus is {{< var glossary.responsible >}} for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
   a. Any decision regarding this rule will be decided by {{< var acronyms.ec >}}.
1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
   a. Brothers will pay all financial obligations through either a physical check made out to “Beta Nu Chapter Theta Chi Fraternity” or a wireless transfer/eCheck.
   a. A brother who pays via other methods (i.e. credit card or Apple Pay) may be subject to a fine of up to 5% of the original paid amount, to be determined by the treasurer.
      i. If a brother wishes to bypass this fee, they must submit a deferment to be approved via @sec-art-OUD16M61, Item 3.
1. Brothers may send a notice directly to the president that they will not be paying dues for the coming semester. One month after this notice has been sent, the brother is automatically suspended.

@@

1. {{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have the right to request access to all accounts, budgeting and financial software, the current ledger, and Greek Bill, excluding bank accounts, subject to the discretion of the treasurer and CAB Treasurer Advisor.
2. {{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have the right to request access to any records or statements from the bank account (or whatever online service is currently being used). 
3. Only the President, Treasurer, and CAB Treasurer Advisor will have access to the bank accounts.

@@

   a. The chair who controls the budget in question.
      i. If the budget is not under a particular chair, or the chair is indisposed, any non-treasurer member of {{< var acronyms.ec >}} may act as a substitute.
      i. If the chair who controls the budget is also the treasurer, any other member of {{< var acronyms.ec >}} may act as a substitute.

### 2025-09-29 src/articles/article7.qmd
sync google docs changes

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a {{< var glossary.simple-majority >}} vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in @sec-art-6GSVIPRZ, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, @sec-art-6GSVIPRZ, Item 3, or @sec-art-6GSVIPRZ, Item 4, they will be brought up for standards by the President, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on {{< var glossary.probation >}}, and becomes {{< var glossary.staggard >}}
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. No candles will be burned inside the house or on the chapter property.
1. @sec-art-6GSVIPRZ, Item 1, @sec-art-6GSVIPRZ, Item 2, and @sec-art-6GSVIPRZ, Item 3 will become null and void upon the downfall of Western Civilization.

@@

1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws ({{< var acronyms.ibl >}}).
   a. The following brothers are exempt from this policy:
      i. 1st year students
      i. Commuter Students
      i. Those who are married
      i. Those who receive housing as compensation for employment (e.g. Resident Assistants)
      i. Those who are on Co-op, Study Abroad, or a similar program
      i. Those who were ineligible or exempt at the beginning of the school year\
      i. Those with a prohibitive medical condition as approved by Case Western Reserve University ({{< var acronyms.cwru >}})

1. The following brothers must live in the chapter house:
   a. President
   a. Vice President
   a. Vice President of Health and Safety
   a. Treasurer
   a. Marshal
   a. Recruitment Chair
   a. Scholarship Chair
   a. House Manager
   a. Food Steward

@@

1. In order for a brother to move into the house, they must not be on {{< var glossary.financial-probation >}} and must not have a debt to the chapter exceeding $3000, including {{< var glossary.deferment >}}s.
   a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.

@@

   a. Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of the Vice President.
      i. The house may not be dropped below capacity.
      i. If this method would bring the house below capacity:\
         1. Of the brothers with the highest {{< var glossary.roster-number >}} among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.

   a. If, after application of the method described in @sec-art-C89656BJ, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
      i. Brothers listed in @sec-art-71TPHUXH, Item 2 cannot be forced to live out of the house.

@@

1. Room 205 is reserved for the President unless they waive this right.

1. Room assignments will be made by the Vice President following these guidelines:

   a. If two or more groups of brothers wish to occupy the same room, the room will be assigned to:
      i. The group with the most brothers, not to exceed the capacity of the room; else
      i. The group of brothers with the greatest number of brothers with {{< var glossary.squatters-rights >}} for that particular room; else
      i. The group of brothers with the lowest aggregate {{< var glossary.roster-number >}}; else
      i. The group of brothers decided by a mutually acceptable method.

>>>>

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a {{< var glossary.simple-majority >}} vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in @sec-art-6GSVIPRZ, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates the above (@sec-art-6GSVIPRZ, Items 1-4), the brother will be brought up for standards, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on {{< var glossary.probation >}}, and becomes {{< var glossary.staggard >}}
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. If a guest violates the above (@sec-art-6GSVIPRZ, Items 1-4), they will be banned from the chapter house and property. This ban may be rescinded by a {{< var glossary.supermajority >}} (2/3) vote of the chapter.
1. No candles will be burned inside the house or on the chapter property.
1. @sec-art-6GSVIPRZ, Items 1-4 will become null and void upon the downfall of Western Civilization.
   a. A necessary (but not sufficient) condition for the downfall of Western Civilization is the dissolution and nullification of these bylaws.
      i. The above item is a Catch-22. No, you cannot do anything about it.

@@

1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws ({{< var acronyms.ibl >}}).
   a. The following brothers are exempt from this policy:
      i. Commuter Students
      i. Those who are married
      i. Those who receive housing as compensation for employment (e.g. Resident Assistants)
      i. Those who are on Co-op, Study Abroad, or a similar program
      i. Those who were ineligible or exempt at the beginning of the school year (e.g. first year students)
      i. Those with a prior binding lease or housing contract that extends into the semester that they would live in the house
      i. Those with a prohibitive medical condition as approved by Case Western Reserve University ({{< var acronyms.cwru >}})

1. All elected members of EC, excepting the President and Treasurer may live out of the house upon being elected, but beginning their first Fall semester in office, must live in the house.
   a. This superseded the exemptions of @sec-art-71TPHUXH, Item 1a
   a. The President and Treasurer must live in house the first full (not necessarily Fall!) semester of their office

1. The following brothers must live in the chapter house. This superseded the exemptions of @sec-art-71TPHUXH, Item 1a:
   a. All elected members of EC (subject to @sec-art-71TPHUXH, Item 2)
   a. House Manager 
   a. Detail manager
   a. Food Steward

@@

1. In order for a brother to move into the house, they must not be on {{< var glossary.financial-probation >}} and must not have a debt to the chapter exceeding $3000, excluding {{< var glossary.deferment >}}s.
   a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.

@@

   a. Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of {{< var acronyms.ec >}}.
      i. This option does not apply to any positions listen in @sec-art-71TPHUXH, Item 3
      i. The house may not be dropped below capacity.
      i. If this method would bring the house below capacity:\
         1. Of the brothers who wish to move out, select the number of brothers that would bring the house to capacity via a mutually acceptable method. If no acceptable method if found, the brothers with the lowest {{< var glossary.roster-number >}}s will move out and the remaining brothers will live in house such that the house is at capacity.

   a. If, after application of the method described in @sec-art-C89656BJ, Item 1a, the house is still above capacity, brothers with the lowest {{< var glossary.roster-number >}} will be forced to move out.
      i. Brothers listed in @sec-art-71TPHUXH, Item 2 cannot be forced to live out of the house.
      i. In the Spring semester, no brother who lived in the house during the Fall semester can be forced to live out of the house via this item (@sec-art-C89656BJ, Item 1b).

@@

1. Room assignments will be made by the Vice President following these guidelines:
   a. If two or more groups of brothers wish to occupy the same room, the room will be assigned to:
      i. The group with the most brothers, not to exceed the capacity of the room; else
      i. The group of brothers with the greatest number of brothers with {{< var glossary.squatters-rights >}} for that particular room; else
      i. The group of brothers with the lowest aggregate {{< var glossary.roster-number >}}; else
      i. The group of brothers decided by a mutually acceptable method.
